---
title: "Climate Change and Conflict"
author: "Luca Frank"
date: "1 3 2022"
output:
  html_document: default
  pdf_document: default
---
#Packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = TRUE, echo = TRUE, error = FALSE, warning = FALSE, message = FALSE)
```

```{r load-packages, results='hide',echo=FALSE}
# Install and load required packages
p_required <- c("tidyverse","ggplot2",  "texreg", "countrycode","readxl","readr","sf","raster","ggmap","tmap","svglite","spatstat","geojson","rgeos","terra","mediation","terra","devtools","pastecs","xtable","ggsci","stargazer")  
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
    install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)

library(tidyverse)
library(ggplot2)
library(ggsci)
library(texreg)
library(countrycode)
library(readxl)
library(readr)
library(sf)
library(raster)
library(ggmap)
library(spatstat)
library(rgeos)
library(mediation)
library(terra)
library(rgdal)
library(devtools)
library(vdemdata)
library(pastecs)
library(xtable)
library(stargazer)
library(broom)
library(haven)


```

# Data Loading
## ACLED
```{r}
#import ACLED Data
acled1 <- read_csv("data/acled/acled1.csv")
acled2 <- read_csv("data/acled/acled2.csv")

acled <- rbind(acled1,acled2)

#convert csv file to shapefile (Coordinate Reference System (CRS) = WGS84 (4326))
acled <- st_as_sf(acled, coords=c("longitude","latitude"), crs = 4326)
```

## Aqueduct 3.0
```{r}
aqua1 <- read_sf("data/Aqueduct/aqua1.gpkg")
aqua2 <- read_sf("data/Aqueduct/aqua2.gpkg")

aqua <- rbind(aqua1,aqua2)
```

##Districts (Admin1)
```{r}
#workaround error
sf::sf_use_s2(FALSE)
#load states shapefile
dis <- read_sf("data/states/ne_10m_admin_1_states_provinces.shp")

dis <- dis %>%
  dplyr::select(name,iso_a2) 

#recode some regions to fit to recognized countries
# dis <- dis %>%
#   mutate(sov_a3 = ifelse(sov_a3=="SDS", "SSD",sov_a3),
#          sov_a3 = ifelse(sov_a3=="SOL", "SOM",sov_a3),
#          sov_a3 = ifelse(sov_a3=="SAH", "MAR",sov_a3))
# 

#load aqua
water <- aqua 

#assign shapefile admin_1 the nearest aqua
dis <- st_join(dis,water,join=st_overlaps,left=TRUE,largest=TRUE)

# dis<- na.omit(dis)
dis <- dis %>%
  mutate(country = countrycode(iso_a2, "iso2c", "country.name")) 

```

```{r}
#acled
riots15 <- acled %>% 
  dplyr::filter(event_type == "Riots",year == 2015) %>% 
  dplyr::select(event_type) 
  
protests15 <- acled %>% 
  dplyr::filter(event_type == "Protests", year == 2015) %>% 
  dplyr::select(event_type) 

conflict5 <- acled %>%
  filter(event_type == "Riots" | event_type == "Protests", year >= 2015, year <= 2020) %>%
  dplyr::select(year, event_type)

conflict5 <- acled %>%
  filter(event_type == "Riots" | event_type == "Protests", year >= 2016, year <= 2021) %>%
  dplyr::select(year, event_type)

#dis <- st_join(dis,conflict,join=st_contains,left=TRUE)

dis$riots15 <- lengths(st_intersects(dis,riots15))
dis$protests15 <- lengths(st_intersects(dis,protests15))
dis$conflict5 <- lengths(st_intersects(dis,conflict5))
```

```{r}
#load african countries ISO/NAME_0
africa <- read_csv("data/africa/Africa_boundaries.csv")

africa_code <- africa %>%
  mutate(africa = TRUE) %>%
  dplyr::select(ISO,africa)%>%
  mutate(ISO=countrycode(ISO,"iso3c","iso2c"))

#filter for africa
dis <- left_join(dis,africa_code, by=c("iso_a2"="ISO"))

#only countries with an agr weight score
dis <- dis %>%
  mutate(africa = ifelse(w_awr_agr_tot_score > 0,TRUE,FALSE)) %>%
  filter(africa == TRUE)

ID <- c(1:924)
dis <- cbind(ID,dis)
```

## Food Insecurity
```{r}
#load csv created by FoodInsecurity.R
dis_sec <- read_csv("data/dis_sec.csv")

dis_sec <- dis_sec %>%
  mutate(food_sec = (sec15+sec16+sec17)/3)

dis <-  left_join(dis,dis_sec, by="ID")
```

##Population Density
```{r}
#density varible name V1
density <- read_csv("data/density.csv")

dis <- cbind(dis,density)

density15 <- read_csv("data/density15.csv")

density15 <- density15 %>%
  rename("ID"="...1", "density15" = "V1")

#add density15 to the dis data 
dis <- left_join(dis,density15, by = "ID")

# calculate the density change from 2015 to 2020
dis <- dis %>%
  mutate(density_change = V1 - density15)
```

##Consumer Prices Indices 
```{r}
#load Consumer Price Indices food (baseline at 2015= 100%)
CPI <- read_csv("data/faostat/ConsumerPriceIndices_E_Africa.csv")

CPI_ISO <- read_xlsx("data/ISO.xlsx")

CPI <- CPI %>%
  filter(Months == "September",Item=="Consumer Prices, Food Indices (2015 = 100)")

CPI <- cbind(CPI,CPI_ISO)
CPI <- CPI %>%
  dplyr::select(ISO,Y2000,Y2001,Y2002,Y2003,Y2004,Y2005,Y2006,
                Y2007,Y2008,Y2009,Y2010,Y2011,Y2012,Y2013,Y2014,
                Y2015,Y2016,Y2017,Y2018,Y2019,Y2020)

#calculate changes of food consumer price per country per Year

CPI <- CPI %>%
  mutate(CPI_2015 = Y2015 - Y2014,
         CPI_2016 = Y2016 - Y2015,
         CPI_2017 = Y2017 - Y2016,
         CPI_2018 = Y2018 - Y2017,
         CPI_2019 = Y2019 - Y2018,
         CPI_2020 = Y2020 - Y2019) %>%
  mutate(CPI3 = CPI_2015+CPI_2016+CPI_2017)%>%
  dplyr::select(ISO, CPI_2015,CPI_2016,CPI_2017,CPI_2018,CPI_2019,CPI_2020,CPI3)

dis <- left_join(dis,CPI, by=c("country"="ISO"))
```

##Catastrophes
```{r}
cata <- read_csv("data/disaster/pend-gdis-1960-2018-disasterlocations.csv")

cata <- st_as_sf(cata, coords=c("longitude","latitude"), crs = 4326)

cata <- cata %>% dplyr::select(year,disastertype)

#droughtsm floods and all catastrohes in the last 5 years 
drought5 <- cata %>%
  filter(disastertype== "drought",year >=2010, year <=2015)
flood5 <- cata %>%
  filter(disastertype == "flood",year >=2010, year <=2015)

cata5 <- cata %>%
  filter(year >=2010, year <=2015)

dis$cata5 <- lengths(st_intersects(dis,cata5))
dis$flood5 <- lengths(st_intersects(dis,flood5))
dis$drought5 <- lengths(st_intersects(dis,drought5))
```

##Vdem Data
```{r}
#install vdem data package
#devtools::install_github("vdeminstitute/vdemdata")

#assign vdem data to vdem 
vdem <- vdem

vdem_15 <- vdem %>%
  dplyr::select(country_name,year,v2x_partipdem,e_gdppc) %>%
  filter(year==2014) %>%
  rename("partipdem" = "v2x_partipdem", "gdp" = "e_gdppc") %>%
  mutate(ISO= countrycode(country_name,"country.name","iso2c")) %>%
  dplyr::select(ISO,partipdem, gdp)


dis <- left_join(dis,vdem_15, by=c("iso_a2"="ISO"))


#select countries with civil wars since 2000
vdem_war <- vdem %>%
  dplyr::select(country_name,year, e_civil_war) %>%
  filter(e_civil_war == 1) %>%
  filter(year >= 2000) %>%
  dplyr::select(country_name) %>%
  distinct() %>%
  mutate(civil = 1,ISO= countrycode(country_name,"country.name","iso2c")) 


dis <- left_join(dis,vdem_war, by=c("iso_a2"="ISO"))

#code countries with civil war since 2000 with 1 else 0
dis <- dis %>%
  mutate(civil = replace_na(dis$civil,0))

dis <- dis %>%
  mutate(civil_cat = ifelse(civil==1, "Civil War","No Civil War"))

```

##State fragility index

```{r}
fsi <- read_xlsx("data/fsi-2014.xlsx")

fsi <- fsi %>%
  dplyr::select(Country, Total) %>%
  mutate(ISO = countrycode(fsi$Country,"country.name","iso3c")) %>%
  rename("fsi" = "Total")

dis <- left_join(dis,fsi,by=c("iso_a2"="ISO"))

```


# Data Analysis
##Describtive statistics
```{r}
dis_stat <- dis %>%
  dplyr::select(w_awr_agr_tot_score,bws_score, bwd_score, drr_score, cata5,flood5, drought5, CPI3,food_sec,conflict5,density_change,density15,partipdem, gdp, fsi, civil)

st_geometry(dis_stat) <- NULL

stargazer(dis_stat)
```

##Moderated Mediation 
###Main Analysis by Table
####Table1 Agriculture Weight 
```{r}
#Agriculture OLS and Poission regression for CPI
agr_cpi_con_1 <- lm(CPI3 ~ w_awr_agr_tot_score+ density15 +  fsi+gdp, data=dis)
agr_cpi_con_2 <- glm(conflict5 ~ CPI3*density_change + w_awr_agr_tot_score+  density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

#Agriculture OLS and Poisson regression fod food security
agr_sec_con_1 <- lm(food_sec ~  w_awr_agr_tot_score+density15 + fsi + gdp, data=dis)
agr_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + w_awr_agr_tot_score+ density15+ partipdem + fsi + civil + gdp, data = dis, family=poisson())


stargazer(agr_cpi_con_1,agr_cpi_con_2,agr_sec_con_1,agr_sec_con_2,
          style="ajps",
          order = "w_awr_agr_tot_score",
          covariate.labels = c("Agr. Score","Food Price","Food Security","Pop. Density Change","Pop. Density","Democracy","FSI","Civil War", "GDP","Food Price: Pop. Density Change","Food Security:Pop. Density Change"),
          title = "Water Stress Effect on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
          )
```



```{r}
#Figure for showing mediation
agr_cpi_con_med <- mediate(agr_cpi_con_1,agr_cpi_con_2, treat = "w_awr_agr_tot_score", mediator = "CPI3",  sims = 1000)

summary(agr_cpi_con_med)


agr_sec_con_med <- mediate(agr_sec_con_1,agr_sec_con_2,treat = "w_awr_agr_tot_score", mediator = "food_sec", sims = 1000)

summary(agr_sec_con_med)

```

####Table2 Catastrophes as IV
```{r}
cata5_cpi_con_1 <- lm(CPI3 ~ cata5+density15 +  fsi+gdp, data=dis)
cata5_cpi_con_2 <- glm(conflict5 ~ CPI3*density_change + cata5 + density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

cata5_sec_con_1 <- lm(food_sec ~ cata5+density15 +  fsi+gdp, data=dis)
cata5_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + cata5 + density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

stargazer(cata5_cpi_con_1,cata5_cpi_con_2,cata5_sec_con_1,cata5_sec_con_2,
          style = "ajps",
          order = "cata5",
          covariate.labels = c("Catastrophes","Food Price", "Food Security","Pop. Density Change","Pop. Density","Democracy", "FSI", "Civil War",  "GDP","Food Price: Pop. Density Change","Food Security: Pop. Density Change"),
          title = "The effect of Catastrophes on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
)

```

```{r}
#Figure for showing mediation
cata5_cpi_con_med <- mediate(cata5_cpi_con_1,cata5_cpi_con_2, treat = "cata5", mediator = "CPI3",  sims = 1000)

summary(cata5_cpi_con_med)


cata5_sec_con_med <- mediate(cata5_sec_con_1,cata5_sec_con_2,treat = "cata5", mediator = "food_sec",sims = 1000)

summary(cata5_sec_con_med)

```

####Appendix tables
```{r}
#BWS

bws_cpi_con_1 <- lm(CPI3 ~ bws_score+density15 +  fsi+gdp, data=dis)
bws_cpi_con_2 <- glm(conflict5 ~ CPI3 *density_change+ bws_score+ + density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

bws_sec_con_1 <- lm(food_sec ~ bws_score+density15 +  fsi+gdp, data=dis)
bws_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + bws_score+ + density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

stargazer(bws_cpi_con_1,bws_cpi_con_2,bws_sec_con_1,bws_sec_con_2 ,
          style = "ajps",
          order = "bws_score",
          covariate.labels = c("Baseline Water Stress","Food Price", "Food Security","Pop. Density Change","Pop. Density","Democracy", "FSI", "Civil War",  "GDP","Food Price: Pop. Density Change","Food Security: Pop. Density Change"),
          title = "Effect of Baseline Water Stress on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
)
```

```{r}
#BWD
bwd_cpi_con_1 <- lm(CPI3 ~ bwd_score+density15 +  fsi+gdp, data=dis)
bwd_cpi_con_2 <- glm(conflict5 ~ CPI3*density_change + bwd_score+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

bwd_sec_con_1 <- lm(food_sec ~ bwd_score+density15 +  fsi+gdp, data=dis)
bwd_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + bwd_score+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

stargazer(bwd_cpi_con_1,bwd_cpi_con_2,bwd_sec_con_1,bwd_sec_con_2,
          style = "ajps",
          order = "bwd_score",
          covariate.labels = c("Baseline Water Depletion","Food Price", "Food Security","Pop. Density Change","Pop. Density","Democracy", "FSI", "Civil War",  "GDP","Food Price: Pop. Density Change","Food Security: Pop. Density Change"),
          title = "Effect of Baseline Water Depletion on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
)

```

```{r}
#DRR
drr_cpi_con_1 <- lm(CPI3 ~ drr_score+density15 +  fsi+gdp, data=dis)
drr_cpi_con_2 <- glm(conflict5 ~ CPI3*density_change + drr_score+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

drr_sec_con_1 <- lm(food_sec ~ drr_score+density15 +  fsi+gdp, data=dis)
drr_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + drr_score+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

stargazer(drr_cpi_con_1,drr_cpi_con_2,drr_sec_con_1,drr_sec_con_2,
          style = "ajps",
          order = "drr_score",
          covariate.labels = c("Drought Risk","Food Price", "Food Security","Pop. Density Change","Pop. Density", "Democracy", "FSI", "Civil War", "GDP","Food Price: Pop. Density Change","Food Security: Pop. Density Change"),
          title = "The effect of Drought Risk on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
)
```

```{r}
#floods
flood_cpi_con_1 <- lm(CPI3 ~ flood5+density15 +  fsi+gdp, data=dis)
flood_cpi_con_2 <- glm(conflict5 ~ CPI3*density_change + flood5+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

flood_sec_con_1 <- lm(food_sec ~ flood5+density15 +  fsi+gdp, data=dis)
flood_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + flood5+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

stargazer(flood_cpi_con_1,flood_cpi_con_2,flood_sec_con_1,flood_sec_con_2,
          style = "ajps",
          order = "flood5",
          covariate.labels = c("Floods","Food Price", "Food Security","Pop. Density Change","Pop. Density","Democracy", "FSI", "Civil War",  "GDP","Food Price: Pop. Density Change","Food Security: Pop. Density Change"),
          title = "The effect of Floods on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
)

```

```{r}
#droughts
drought_cpi_con_1 <- lm(CPI3 ~ drought5+density15 +  fsi+gdp, data=dis)
drought_cpi_con_2 <- glm(conflict5 ~ CPI3*density_change + drought5+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

drought_sec_con_1 <- lm(food_sec ~ drought5+density15 +  fsi+gdp, data=dis)
drought_sec_con_2 <- glm(conflict5 ~ food_sec*density_change + drought5+ density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

stargazer(drought_cpi_con_1,drought_cpi_con_2,drought_sec_con_1,drought_sec_con_2,
          style = "ajps",
          order = "drought5",
          covariate.labels = c("Droughts","Food Price", "Food Security","Pop. Density Change","Pop. Density", "Democracy", "FSI", "Civil War",  "GDP","Food Price: Pop. Density Change","Food Security: Pop. Density Change"),
          title = "The effect of Droughts on Conflict mediated by Food Consumer Price Index and Food Security and moderated by the Population Density Change"
)

```
#Prediction

```{r}
dis <- dis %>%
  rename("ws" = "w_awr_agr_tot_score")

model <- glm(conflict5 ~ CPI3*density_change + ws+  density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())
summary(model)

# Minimum seat share
min_ws <- min(dis$ws) 
# Maximum seat share
max_ws <- max(dis$ws)
#sepcify scenario
df_scenario_2 <- tibble(
                   CPI3 = mean(dis$CPI3,na.rm=TRUE),
                   density_change = mean(dis$density_change,na.rm=TRUE),
                   ws = seq(min_ws, max_ws, by = 0.01), # min & max party size
                   density15 = median(dis$density15,na.rm=TRUE),
                   partipdem = mean(dis$partipdem,na.rm=TRUE),
                   fsi = mean(dis$fsi,na.rm=TRUE),
                   civil = mean(dis$civil,na.rm=TRUE),
                   gdp = mean(dis$gdp,na.rm=TRUE),
                   )

df_scenario <- tibble(
                   CPI3 = mean(dis$CPI3,na.rm=TRUE),
                   density_change = mean(dis$density_change,na.rm=TRUE),
                   ws = c(min_ws, max_ws), # min & max party size
                   density15 = median(dis$density15,na.rm=TRUE),
                   partipdem = mean(dis$partipdem,na.rm=TRUE),
                   fsi = mean(dis$fsi,na.rm=TRUE),
                   civil = mean(dis$civil,na.rm=TRUE),
                   gdp = mean(dis$gdp,na.rm=TRUE),
                   )

# get predictions for the scenario of interest
pred_values <- predict(model, newdata = df_scenario_2, type = "response", se.fit = FALSE)
pred_values
# rounded
pred_values %>% round(2)



# Let's bind seatshare range and predicted values together
toplot <- bind_cols(
  # our data on the x-axis
  ws = df_scenario_2$ws
  # our data on the y-axis
  , pred_val = pred_values)

# Multiple values by 100 for a more intuitive presentation
# toplot <- toplot %>% 
#   mutate(ws = ws*100
#          , pred_val = pred_val*100
#          )

summary(model)

#model <- model%>%tidy()

# Plot
ggplot(toplot) + 
  geom_jitter(aes(x = ws, y = pred_val),width=mean(model$std.error)*5,height=0,alpha=.5) + 
  geom_line(aes(x = ws, y = pred_val),size=1,color="darkgreen",alpha=.6) + 
  theme_minimal() + 
  labs(x = "Water Score Agr. Weight", y = "Conflict events per state/district"
       , title = "Effect of water stress on Conflict per state")

#from session 10
model <- glm(conflict5 ~ CPI3*density_change + ws+  density15 + partipdem + fsi + civil  + gdp, data = dis, family=poisson())

model %>% tidy() %>%
  mutate(conf.low = estimate - qnorm(0.975) * std.error
        , conf.high = estimate + qnorm(0.975) * std.error) 

# Minimum seat share
min_ws <- min(dis$ws) 
# Maximum seat share
max_ws <- max(dis$ws)
# over the range of seat shares as observed in our data
df_scenario <- tibble(
                   CPI3 = mean(dis$CPI3,na.rm=TRUE),
                   density_change = mean(dis$density_change,na.rm=TRUE),
                   ws = seq(min_ws, max_ws, by = 0.1), # min & max party size
                   density15 = median(dis$density15,na.rm=TRUE),
                   partipdem = mean(dis$partipdem,na.rm=TRUE),
                   fsi = mean(dis$fsi,na.rm=TRUE),
                   civil = mean(dis$civil,na.rm=TRUE),
                   gdp = mean(dis$gdp,na.rm=TRUE),
                   )

# Store predicted mean response
# ===========================
df_expected <- predict(model, new = df_scenario, interval =  "confidence") %>% 
  as_tibble() 

# merge the corresponding scenario data to the predicted values
# ===========================
toplot <- df_expected %>%
  bind_cols(df_scenario)

# Plot , what is fit? lwr ? upr? where are they from
# ===========================
ggplot(toplot) + 
  geom_line(aes(ws, value)) +
  #geom_ribbon(aes(ws, value),  alpha = 0.2) +
  theme_minimal() + 
  labs(y = "Expected value", x = "seat share", title = "Expected values of government opposition", subtitle = "Conditional on party size") 
```


#Visualizations
```{r, eval=FALSE}
#conflict development
cot <- acled %>%
  filter(event_type =="Protests" | event_type=="Riots") %>%
  dplyr::select(year, event_type,country,region) 

st_geometry(cot) <- NULL

cot <- cot %>%
  group_by(year,country) %>%
  count(event_type)

acled_region <- acled %>%
  dplyr::select(country,region) %>%
  distinct()

cot <- left_join(cot,acled_region,by="country")

ggplot(cot, aes(year,n,color=region)) +
  geom_smooth(method = 'glm', method.args = list(family = 'poisson'))+
  labs(y = "Protests and Riots", x = "Year",
    title = "Amount of Protests and Riots per Year",
       color = "Region")+
  scale_color_uchicago()+
  theme(
    legend.position="bottom")+
  theme_bw()

#ggsave("ConflictDevAfrica.png",width=16, height=9,units="cm",dpi=1000)
  
```
##Appendix Maps
```{r,eval=FALSE}
#aqueduct variables
ggplot() +
  geom_sf(data=dis,aes(fill=bws_score))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Baseline \nWater \nStress",
       title= "Baseline Water Stress in Africa per district"
  )+
  theme_bw()+
  theme()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("bws.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=bwd_score))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Baseline \nWater \nDepletion",
       title= "Baseline Water Depletion in Africa per district"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("bwd.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=drr_score))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Drought \nRisk",
       title= "Drought Risk in Africa per district"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("drr.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=w_awr_agr_tot_score))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Agriculture \nWater \nStress",
       title= "Agriculture weighted Water Stress in Africa per district"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("agr.png",width=16, height=16,units="cm",dpi=1000)


#catastrophes
ggplot() +
  geom_sf(data=dis,aes(fill=cata5))+
  scale_fill_viridis_c(direction=1,option="viridis",trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Number of \nCatastrophes",
       title= "Floods and Droughts in Africa per district", 
       subtitle = "From 2010 - 2015"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
                        
ggsave("cata.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data = dis %>% filter(flood5 > 20))+
  geom_sf(data=dis %>% filter(flood5 < 20),aes(fill=flood5))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Number of \nFloods",
       title= "Floods in Africa per district", 
       subtitle = "From 2010 - 2015 (without Outlier)"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("bws.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis ,aes(fill=flood5))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Number of \nFloods",
       title= "Floods in Africa per district", 
       subtitle = "From 2010 - 2015 "
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("flood.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=drought5))+
  scale_fill_viridis_c(direction=1,option="viridis") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Number of \nDroughts",
       title= "Droughts in Africa per district", 
       subtitle = "From 2010 - 2015"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("drought.png",width=16, height=16,units="cm",dpi=1000)


#Food Consumer Price Index
ggplot() +
  geom_sf(data=dis,aes(fill=CPI3))+
  scale_fill_viridis_c(direction=1,option="viridis",trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Price Increase \nin Percent",
       title= "Food Prices Increase in Africa", 
       subtitle = "From 2015-2017"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("cpi.png",width=16, height=16,units="cm",dpi=1000)


#Food Insecurity
ggplot() +
  geom_sf(data=dis,aes(fill=food_sec))+
  scale_fill_viridis_c(direction=1,option="viridis",trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Food Insecurity \nScale",
       title= "Food Insecurity in Africa", 
       subtitle = "From 2015-2017"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("sec.png",width=16, height=16,units="cm",dpi=1000)


#Conflict
ggplot() +
  geom_sf(data=dis,aes(fill=conflict5))+
  scale_fill_viridis_c(direction=1,option="viridis",trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Number of Events",
       title= "Protests and Riots in Africa", 
       subtitle = "From 2016-2021"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("conflict.png",width=16, height=16,units="cm",dpi=1000)


#control variables
ggplot() +
  geom_sf(data=dis,aes(fill=partipdem))+
  scale_fill_viridis_c(direction=1,option="viridis",trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(fill= "Democracy Score",
       title= "State of Participatory Democracies in Africa", 
       subtitle = "Year 2014"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("dem.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=civil_cat))+
   scale_fill_viridis_d(option = "V",direction=-1,begin=0) +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(title= "Countries that experienced a Cvil War since 2000",
       fill=""
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("civil.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=gdp))+
   scale_fill_viridis_c(option = "V",direction=1,trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(title= "GDP per Capita in Africa",
       subtitle = "Year 2014",
       fill="GDP"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("gdp.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=V1),color=NA)+
   scale_fill_viridis_c(option = "V",direction=1,trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(title= "Population Density per adminstrative subdivision",
       subtitle = "Year 2020",
       fill="Population \nDensity"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("density.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=density_change),color=NA)+
   scale_fill_viridis_c(option = "V",direction=1,trans="log") +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(title= "Population Density Change per adminstrative subdivision",
       subtitle = "From 2015 to 2020",
       fill="People per \nsquared Km"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("density_change.png",width=16, height=16,units="cm",dpi=1000)


ggplot() +
  geom_sf(data=dis,aes(fill=fsi))+
   scale_fill_viridis_c(option = "V",direction=1) +
  coord_sf(xlim=c(-17,50), ylim=c(-33,35), expand = TRUE)+
  labs(title= "Fragility State Index per Country",
       subtitle = "Year 2014",
       fill="FSI Index"
  )+
  theme_bw()+
  theme(
    legend.position=c(.2,.27)
  )
ggsave("fsi.png",width=16, height=16,units="cm",dpi=1000)
```
